Summarize coverage

### 2016-12-20 analysis/plot_cdf_eg.Rmd
Stopping here with revisions to analysis/*.Rmd files due to issue with missing columns in data frames in res.RData; will post issue.

```{r chunk_options, include=FALSE}
library(plyr)
library(dplyr)
library(dscr)
library(magrittr)
library(ashr)
library(ggplot2)
source("chunk-options.R")
source("../code/dsc-shrink/methods/mixfdr.wrapper.R")
source("../R/set_plot_colors.R")
```

```{r}
load("../output/dsc-shrink-files/res.RData")

@@

plot_mean_cdf = function(SEEDS,PLOTMETHODS=c("ash.n","ash.u","ash.hu","truth","mixfdr.tnull"),
      PLOTSCENARIOS=c("spiky","near-normal","flat-top","skew","big-normal","bimodal"),pi0filter=FALSE,...){
  PLOTNAMES=PLOTSCENARIOS
  #set up dataframe with cdf for all methods and all datasets
  df= expand.grid(seed=SEEDS,scenario=PLOTSCENARIOS, method=PLOTMETHODS,stringsAsFactors = FALSE)
  df.cdf=ddply(df,.(seed,scenario,method), get_cdf)

@@

plot_mean_cdf_with_npmle(1,PLOTMETHODS=c("truth","ash.hu"),PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew","big-normal","bimodal")) + facet_wrap(~ scenario, nrow=2)

```

>>>>

```{r chunk_options, include=FALSE}
library(plyr)
library(dplyr)
library(magrittr)
library(ashr)
library(ggplot2)
library(dscr)
source("chunk-options.R")
source("../code/dsc-shrink/methods/mixfdr.wrapper.R")
source("../R/set_plot_colors.R")
```

*Explain here what this chunk does.*

```{r chunk_label}
load("../output/dsc-shrink-files/res.RData")

@@

plot_mean_cdf = function(SEEDS,PLOTMETHODS=c("ash.n","ash.u","ash.hu","truth","mixfdr.tnull"),
      PLOTSCENARIOS=c("spiky","near-normal","flat-top","skew","bimodal"),pi0filter=FALSE,...){
  PLOTNAMES = PLOTSCENARIOS
  #set up dataframe with cdf for all methods and all datasets
  df= expand.grid(seed=SEEDS,scenario=PLOTSCENARIOS, method=PLOTMETHODS,stringsAsFactors = FALSE)
  df.cdf=ddply(df,.(seed,scenario,method), get_cdf)

@@

plot_mean_cdf_with_npmle(1,PLOTMETHODS=c("truth","ash.hu"),PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew","big-normal","bimodal")) + facet_wrap(~ scenario, nrow=2)
```

### 2016-12-20 analysis/plot_egdens.Rmd
Stopping here with revisions to analysis/*.Rmd files due to issue with missing columns in data frames in res.RData; will post issue.

```{r chunk_label}
load("../output/dsc-shrink-files/res.RData")
PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew","bimodal")
PLOTNAMES     = PLOTSCENARIOS

>>>>

```{r retrieve_sim_results}
load("../output/dsc-shrink-files/res.RData")
PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew","bimodal")
PLOTNAMES     = PLOTSCENARIOS

### 2016-12-20 analysis/plot_lfsr.Rmd
Stopping here with revisions to analysis/*.Rmd files due to issue with missing columns in data frames in res.RData; will post issue.

#' @param df dataframe of scores for many methods/scenrios etc
#' @return tall dataframe with columns of scores for each method and the "goldmethod" against which plot is to be made
process_score_for_plotting_against_gold=function(df,PLOTMETHODS=c("ash.n","ash.u","ash.hu"),
                                                 GOLDMETHOD="bayes",PLOTSEEDS=1:100,
                                                 PLOTSCENARIOS=c("spiky","near-normal","flat-top","skew","big-normal","bimodal"),
                                                 PLOTNAMES=PLOTSCENARIOS){
  df %<>% filter(seed %in% PLOTSEEDS) %>% filter(scenario %in% PLOTSCENARIOS) %>% filter(method %in% c(PLOTMETHODS,GOLDMETHOD))
  df$scenario = factor(df$scenario,levels=PLOTSCENARIOS)
  levels(df$scenario)= PLOTNAMES
  #create tall version of dataframe
  df %<>% dplyr::select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    reshape2::melt(id.vars=c("method","scenario","seed",".id"),value.name="val")
  #separate bayes and remainder
  df.bayes = df %>% filter(method==GOLDMETHOD)
  df.rest = df %>% filter(method!=GOLDMETHOD)

>>>>

#' @param df dataframe of scores for many methods/scenrios etc
#' @return tall dataframe with columns of scores for each method and the "goldmethod" against which plot is to be made
process_score_for_plotting_against_gold=function(df,PLOTMETHODS=c("ash.n","ash.u","ash.hu"),
                                                 GOLDMETHOD="bayes",PLOTSEEDS=1:100,
                                                   PLOTSCENARIOS=c("spiky","near-normal","flat-top","skew","big-normal","bimodal")
  PLOTNAMES=PLOTSCENARIOS
  df %<>% filter(seed %in% PLOTSEEDS) %>% 
    filter(scenario %in% PLOTSCENARIOS) %>% 
    filter(method %in% c(PLOTMETHODS,GOLDMETHOD))
  df$scenario = factor(df$scenario,levels=PLOTSCENARIOS)
  levels(df$scenario)= PLOTNAMES
  #create tall version of dataframe
  df %<>% dplyr::select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    reshape2::melt(id.vars=c("method","scenario","seed",".id"),value.name="val")
  #separate bayes and remainder
  df.bayes = df %>% filter(method==GOLDMETHOD)
  df.rest = df %>% filter(method!=GOLDMETHOD)

### 2016-12-20 analysis/summarize_coverage.Rmd
Rendered referee_uaza.html and fixed chunk-options label to chunk_options.
Stopping here with revisions to analysis/*.Rmd files due to issue with missing columns in data frames in res.RData; will post issue.

```{r chunk-options, include=FALSE}
source("chunk-options.R")
```

---
title: "Summarize Coverage"
output: html_document
---

```{r}
load("../output/dsc-shrink-files/res.RData")
coverthresh = 0.05 # threshold at which we look at coverage
findthresh=0.95 #threshold at we define a discovery significant
library("dscr")
library("ashr")
library(reshape2)
library(ggplot2)
library(dplyr)

>>>>

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(dscr)
library(ashr)
library(reshape2)
library(ggplot2)
library(dplyr)
source("chunk-options.R")
```

```{chunk_label r}
load("../output/dsc-shrink-files/res.RData")
coverthresh = 0.05 # threshold at which we look at coverage
findthresh  = 0.95 # threshold at we define a discovery significant
